Time Series Analysis of Chaotic Dynamical Systems with Recurrent Neural Networks

### 2019-04-17 doc/paper/paper.tex

@@

The chaotic behavior of the Lorenz model dictates which wing the
trajectory will follow. This is difficult for the ESN to be able to
model. However, it is possible that I am not using enough data to train
the ESN, and due to resource limitations, I may have not been able to find
the correct parameters to achieve a more perfect performance.

@@

\subsubsection{Double Pendulum}
\subsubsection{Restricted Circular 3 Body}

>>>>

To integrate the model, I use the initial conditions:
$(x_0, y_0, z_0) = (-13.78990503, -11.6069343, 36.17332518)$. The calculated Lyapunov value was $0.9348566$.

@@

The chaotic behavior of the Lorenz model dictates which wing the
trajectory will follow. This is difficult for the ESN to be able to
model. However, it is possible that I am not using enough data to train
the ESN, and due to resource limitations, I may have not been able to find
the correct parameters to achieve a better performance.

@@

\subsubsection{Double Pendulum}

\subsubsection{Restricted Circular 3 Body}
